Distinguishing Between Spin-Aligned and Isotropic Binary Black Hole Populations Using Gravitational Wave Observations

### 2017-03-27 paper/AlignedIsotropicGW.tex
Added text for mass ratio sensitivity.

Figure \ref{fig:O1-posteriors} shows an approximation to the posterior
inferred on $\chieff$ for the three likely \ac{GW} detections
GW150914, GW151226 and LVT151012 from \citet{O1-BBH}.  Because samples
drawn from the posterior on $\chieff$ are not publicly released at
this time, we have approximated the posterior as a Gaussian
distribution with the same mean and 90\% credible interval as quoted
in \citet{O1-BBH}.  There is essentially no posterior support for
$\chieff \gtrsim 0.5$ as observed in the majority of the
electromagnetically-detected stellar-mass black hole population.

@@

\will{Some plots go here showing how the distribution changes as a
  function of mass ratio.}

>>>>

Figure \ref{fig:O1-posteriors} shows an approximation to the posterior
inferred on $\chieff$ for the three likely \ac{GW} detections
GW150914, GW151226 and LVT151012 from \citet{O1-BBH}.  Because samples
drawn from the posterior on $\chieff$ are not publicly released at
this time, we have approximated the posterior as a Gaussian
distribution with the same mean and 90\% credible interval as quoted
in \citet{O1-BBH}.  There is essentially no posterior support for
$\chieff \gtrsim 0.5$ as observed in the majority of the
electromagnetically-detected stellar-mass black hole population.  The
hierarchical modelling is relatively insensitive to the precise
details of the posterior distributions, unlike single-source analysis;
notably our approximation does permit $\chieff = 0$ for GW151226 while
the true posterior rules this out at high confidence
\citep{2016PhRvL.116x1103A,O1-BBH}.

@@

Figure \ref{fig:mass-ratio-sensitivity} shows the distributions of
$\chieff$ that would obtain with a mass ratio $q = m_2/m_1 = 0.5$
compared to the distributions with $q = 1$ used above.  The details of
the distribution are sensitive to the mass ratio, but in our analysis
we are primarily sensitive to the changing \emph{sign} of $\chieff$
under the isotropic models.  This latter property is insensitive to
mass ratio.  As an example, the distinction between the three
different spin amplitude distributions under ten additional detections
is quite weak compared to the aligned/isotropic distinction in Figure
\ref{fig:O2-predictions}.  The differences in the $\chieff$
distribution between $q = 1$ and $q = 0.5$ are even smaller than the
differences between the different magnitude distributions.

\begin{figure}
  \plotone{../plots/chi-eff-distributions-q05}
  \caption{Distributions of $\chieff$ assuming all merging black holes
    have equal masses ($q=1$) or a 2:1 mass ratio ($q = 0.5$).  The
    details of the distribution are sensitive to the mass ratio, but
    in our analysis we are primarily sensitive to the changing
    \emph{sign} of $\chieff$ under the isotropic models.  This latter
    property is unchanged under changing mass ratio.}
  \label{fig:mass-ratio-sensitivity}
\end{figure}
